---
title: "Analyze VA reservoir fDOM 4casts"
author: "Dexter Howard"
date: "2024-09-06"
output: html_document
---

```{r}
library(tidyverse)
library(patchwork)
```



## Read in data and format 

```{r}
#read in scores 
Scored_forecasts <- read_csv("../Data/allReservoir_allmodel_4cast_Scores_30jan25.csv") |> 
  ## filter(reference_datetime >= ymd("2023-07-31"),
  ##        reference_datetime <= ymd("2024-08-01")) |> # Aug 23 - July 24
    # filter(reference_datetime >= ymd("2023-12-01"),
    #      reference_datetime <= ymd("2024-11-30")) |>  #Dec 23 - Nov 24
    #  filter(reference_datetime != ymd("2023-12-28")) |> #fixes insane CCR NNETAR spikes
  filter(reference_datetime >= ymd("2024-03-01"),
         reference_datetime <= ymd("2025-02-28")) |>
  mutate(Horizon = datetime - reference_datetime) |> 
  filter(Horizon > 0, Horizon < 35) |>
  mutate(site_id = ifelse(site_id == "bvre", "BVR", site_id),
         site_id = ifelse(site_id == "fcre", "FCR", site_id),
         site_id = ifelse(site_id == "ccre", "CCR", site_id)) |> 
  mutate(model_id = ifelse(model_id == "fable_persistence", "Persistence", model_id),
         model_id = ifelse(model_id == "climatology", "DOY", model_id),
         model_id = ifelse(model_id == "fDOM_AR_dwh", "TS_AR", model_id),
         model_id = ifelse(model_id == "fDOM_RainLag_dwh", "TS_Rain", model_id),
         model_id = ifelse(model_id == "fDOM_MetRegression_dwh", "TS_Met", model_id),
         model_id = ifelse(model_id == "fableNNETAR", "NNAR", model_id)
         ) |>  #update model names for plotting
    mutate(model_type = ifelse(model_id %in% c("Persistence", "DOY"), "Baseline", "Data Driven")
         ) #grouping by model types


#set model colors and shapes
model_colors <- c("TS_AR" = "#CC6677", "DOY" = "#88CCEE", "Persistence" = "#DDCC77", "NNAR" = "#117733", "TS_Rain" = "#332288", "TS_Met" = "#888888")
model_shape <- c("Data Driven" = 1, "Baseline" = 4)

```


## Checks on missing data and forecasts 


explore missing AR day 

```{r}

AR <- Scored_forecasts |> filter(model_id == "TS_AR")

#no observation
AR_na <- AR |> filter(is.na(observation))
missdateslist <- unique(AR_na$datetime)
AR_na2 <- AR_na |> filter(datetime %in% missdateslist)

#no forecast mean
ARmeanNA <- AR |> filter(is.na(mean))
unique(ARmeanNA$reference_datetime)

```



explore DOY issues 

```{r}
doy <- Scored_forecasts |> filter(model_id == "DOY")

doy_na <- doy |> filter(is.na(crps))
unique(doy_na$datetime)

per <- Scored_forecasts |> filter(model_id == "Persistence")


doy2 <- doy |> filter(Horizon == 1)

doy3 <- doy2 |> filter(is.na(crps))

unique(doy3$reference_datetime)

doy4 <- doy2 |> filter(is.na(mean))

doy5 <- doy2 |> filter(is.na(observation))


```



## RMSE and Skills Plots 


RMSE and faceted metrics over horizon

```{r}

## Set up data for RMSE horizon plot
a <- Scored_forecasts |> 
  group_by(Horizon, site_id, model_id, model_type) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 1)) 

# add a panel for across reservoirs 
b <- Scored_forecasts |> 
  group_by(Horizon, model_id, model_type) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 1)) |> 
  mutate(site_id = "Across Sites")


## Set up data for all metrics SI figure
c <- Scored_forecasts |> 
   group_by(site_id, model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |> 
  pivot_longer(-c(1:4))

# make panel for all sites average
d <- Scored_forecasts |> 
   group_by(model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |> 
  pivot_longer(-c(1:3)) |> 
  mutate(site_id = "Across Sites")


#### Make SI figure 

SI_all_metrics_over_horizon <- rbind(c,d) |> 
  filter(!name %in% c("MAE")) |> 
ggplot(aes(x = Horizon, y = value, color = model_id, linetype = model_type))+
  geom_line(linewidth = 1.2)+
  facet_grid(name~factor(site_id, levels = c("Across Sites","BVR", "CCR", "FCR")), scales = "free_y")+
  labs(x = "Horizon", y = "Metric (QSU)")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 12))+
    # scale_x_continuous(breaks = c(1,4,7,10,13, 16))+
  guides(linetype = guide_legend(nrow = 2))+
  theme(legend.text = element_text(size = 8), legend.title = element_text(size = 10),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = model_colors)+  scale_linetype_manual(values = model_shape)

SI_all_metrics_over_horizon

#ggsave("../Figures/SI_allmetrics_Horizon.png", SI_all_metrics_over_horizon, height = 6, width = 6, units = "in")

```



Skill and associated SI figure 

```{r}

#### Set up data frames by metric and null 

##CRPS Persist
#by reservoir
skill_crps_persist_a <- Scored_forecasts |> 
  select(reference_datetime, datetime, Horizon, site_id, model_id, crps) |> 
  pivot_wider(names_from = model_id, values_from = crps) |> 
  mutate(Skill_AR_crps_P = 1-(TS_AR/Persistence),
         Skill_NNETAR_crps_P = 1-(NNAR/Persistence),
         Skill_MetRegress_crps_P = 1-(TS_Met/Persistence),
         Skill_RainLag_crps_P = 1-(TS_Rain/Persistence)) |> 
  select(site_id, Horizon, Skill_AR_crps_P:Skill_RainLag_crps_P) |> 
  pivot_longer(-c(1:2)) |> 
  group_by(site_id, Horizon, name) |> 
  summarise(value = mean(value, na.rm = T))

#across sites
skill_crps_persist_b <- Scored_forecasts |> 
  select(reference_datetime, datetime, Horizon, site_id, model_id, crps) |> 
  pivot_wider(names_from = model_id, values_from = crps) |> 
  mutate(Skill_AR_crps_P = 1-(TS_AR/Persistence),
         Skill_NNETAR_crps_P = 1-(NNAR/Persistence),
         Skill_MetRegress_crps_P = 1-(TS_Met/Persistence),
         Skill_RainLag_crps_P = 1-(TS_Rain/Persistence)) |> 
  select(site_id, Horizon, Skill_AR_crps_P:Skill_RainLag_crps_P) |> 
  pivot_longer(-c(1:2)) |> 
  group_by(Horizon, name) |> 
  summarise(value = mean(value, na.rm = T)) |> 
  mutate(site_id = "Across Sites")

#bind
skill_crps_persist <- rbind(skill_crps_persist_a, skill_crps_persist_b)

##CRPS Clim
#by res
skill_crps_clim_a <- Scored_forecasts |> 
  select(reference_datetime, datetime, Horizon, site_id, model_id, crps) |> 
  pivot_wider(names_from = model_id, values_from = crps) |> 
  mutate(Skill_AR_crps_C = 1-(TS_AR/DOY),
         Skill_NNETAR_crps_C = 1-(NNAR/DOY),
         Skill_MetRegress_crps_C = 1-(TS_Met/DOY),
         Skill_RainLag_crps_C = 1-(TS_Rain/DOY)) |> 
  select(site_id, Horizon, Skill_AR_crps_C:Skill_RainLag_crps_C) |> 
  pivot_longer(-c(1:2)) |> 
  group_by(site_id, Horizon, name) |> 
  summarise(value = mean(value, na.rm = T))

#across sites
skill_crps_clim_b <- Scored_forecasts |> 
  select(reference_datetime, datetime, Horizon, site_id, model_id, crps) |> 
  pivot_wider(names_from = model_id, values_from = crps) |> 
  mutate(Skill_AR_crps_C = 1-(TS_AR/DOY),
         Skill_NNETAR_crps_C = 1-(NNAR/DOY),
         Skill_MetRegress_crps_C = 1-(TS_Met/DOY),
         Skill_RainLag_crps_C = 1-(TS_Rain/DOY)) |> 
  select(site_id, Horizon, Skill_AR_crps_C:Skill_RainLag_crps_C) |> 
  pivot_longer(-c(1:2)) |> 
  group_by(Horizon, name) |> 
  summarise(value = mean(value, na.rm = T)) |> 
  mutate(site_id = "Across Sites")

skill_crps_clim <- rbind(skill_crps_clim_a, skill_crps_clim_b)

##RMSE Persist
#by res
skill_rmse_persist_a <- Scored_forecasts |> 
   group_by(site_id, model_id, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2)
            ) |> 
  select(Horizon, site_id, model_id, RMSE) |> 
  pivot_wider(names_from = model_id, values_from = RMSE) |> 
  mutate(Skill_AR_rmse_P = 1-(TS_AR/Persistence),
         Skill_NNETAR_rmse_P = 1-(NNAR/Persistence),
         Skill_MetRegress_rmse_P = 1-(TS_Met/Persistence),
         Skill_RainLag_rmse_P = 1-(TS_Rain/Persistence)) |> 
  select(site_id, Horizon, Skill_AR_rmse_P:Skill_RainLag_rmse_P) |> 
  pivot_longer(-c(1:2))

#acorss sites
skill_rmse_persist_b <- Scored_forecasts |> 
   group_by(model_id, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2)
            ) |> 
  select(Horizon, model_id, RMSE) |> 
  pivot_wider(names_from = model_id, values_from = RMSE) |> 
  mutate(Skill_AR_rmse_P = 1-(TS_AR/Persistence),
         Skill_NNETAR_rmse_P = 1-(NNAR/Persistence),
         Skill_MetRegress_rmse_P = 1-(TS_Met/Persistence),
         Skill_RainLag_rmse_P = 1-(TS_Rain/Persistence)) |> 
  select(Horizon, Skill_AR_rmse_P:Skill_RainLag_rmse_P) |> 
  pivot_longer(-c(1)) |> 
  mutate(site_id = "Across Sites")

skill_rmse_persist <- rbind(skill_rmse_persist_a, skill_rmse_persist_b)

##RMSE Clim
#by res
skill_rmse_clim_a <- Scored_forecasts |> 
   group_by(site_id, model_id, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2)
            ) |> 
  select(Horizon, site_id, model_id, RMSE) |> 
  pivot_wider(names_from = model_id, values_from = RMSE) |> 
  mutate(Skill_AR_rmse_C = 1-(TS_AR/DOY),
         Skill_NNETAR_rmse_C = 1-(NNAR/DOY),
         Skill_MetRegress_rmse_C = 1-(TS_Met/DOY),
         Skill_RainLag_rmse_C = 1-(TS_Rain/DOY)) |> 
  select(site_id, Horizon, Skill_AR_rmse_C:Skill_RainLag_rmse_C) |> 
  pivot_longer(-c(1:2))

#across sites
skill_rmse_clim_b <- Scored_forecasts |> 
   group_by(model_id, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2)
            ) |> 
  select(Horizon, model_id, RMSE) |> 
  pivot_wider(names_from = model_id, values_from = RMSE) |> 
  mutate(Skill_AR_rmse_C = 1-(TS_AR/DOY),
         Skill_NNETAR_rmse_C = 1-(NNAR/DOY),
         Skill_MetRegress_rmse_C = 1-(TS_Met/DOY),
         Skill_RainLag_rmse_C = 1-(TS_Rain/DOY)) |> 
  select(Horizon, Skill_AR_rmse_C:Skill_RainLag_rmse_C) |> 
  pivot_longer(-c(1))|> 
  mutate(site_id = "Across Sites")

skill_rmse_clim <- rbind(skill_rmse_clim_a, skill_rmse_clim_b)


#### Put data frames together 
skill_df <- rbind(skill_crps_clim, skill_crps_persist, skill_rmse_clim, skill_rmse_persist) |> 
  mutate(name_a = name) |>  #make a copy of name for reference
  select(site_id, Horizon, name_a, name, value) |> 
  tidyr::separate(name, into = c("Skill", "model_id", "metric", "Null"), sep = "_") |>  #break apart name column for grouping 
  mutate(Null = ifelse(Null == "P", "Skill_Peristence", "Skill_Climatology")) |> 
  mutate(model_idA = ifelse(model_id == "AR", "TS_AR", NA),
         model_idA = ifelse(model_id == "NNETAR", "NNAR", model_idA),
         model_idA = ifelse(model_id == "MetRegress", "TS_Met", model_idA),
         model_idA = ifelse(model_id == "RainLag", "TS_Rain", model_idA)) #fix model names to match above




#### Make plots 
#Skill CRPS 
skill_crps_plot <- skill_df |> 
  filter(metric == "crps") |> 
  mutate(NullA = ifelse(Null == "Skill_Climatology", "DOY", "Persistence")) |> 
  #filter(!site_id == "Across Sites") |> 
  ggplot(aes(x = Horizon, y = value, color = model_idA))+
  geom_line()+
  facet_grid(NullA~factor(site_id, levels = c("Across Sites", "BVR", "CCR", "FCR")), scales = "free_y")+
  geom_hline(yintercept = 0, linewidth =1.2, linetype = 2)+
  geom_line(linewidth = 1.2)+
  # scale_x_continuous(breaks = c(1,4,7,10,13,16))+ 
  guides(colour = guide_legend(nrow = 1))+
  labs(x = "Horizon", color = "model", title = "b) CRPS Skill")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 14),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = model_colors)

#Skill RMSE
skill_rmse_plot <- skill_df |> 
  filter(metric == "rmse") |> 
  mutate(NullA = ifelse(Null == "Skill_Climatology", "DOY", "Persistence")) |> 
  #filter(!site_id == "Across Sites") |> 
  ggplot(aes(x = Horizon, y = value, color = model_idA))+
  geom_line()+
  facet_grid(NullA~factor(site_id, levels = c("Across Sites", "BVR", "CCR", "FCR")), scales = "free_y")+
  geom_hline(yintercept = 0, linewidth =1.2, linetype = 2)+
  geom_line(linewidth = 1.2)+
  # scale_x_continuous(breaks = c(1,4,7,10,13,16))+ 
  guides(colour = guide_legend(nrow = 1))+
  labs(x = "Horizon", color = "model", title = "a) RMSE Skill")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 14),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = model_colors)


#panel 

all_skill_SI <- skill_rmse_plot / skill_crps_plot

all_skill_SI
#ggsave("../Figures/all_skill_SI.png", all_skill_SI, height = 8, width = 6, units = "in")


```

RMSE combined plot 

```{r}

#RMSE horizon plot
rmse_for_join <- rbind(a,b) |> 
  ggplot(aes(x = Horizon, y = RMSE, color = model_id, linetype = model_type))+ #, linetype = model_type
  geom_line(linewidth = 1.2)+
  facet_wrap(~factor(site_id, levels = c("Across Sites", "BVR", "CCR", "FCR")), scales = "fixed", ncol = 4)+
  # scale_x_continuous(breaks = c(1,4,7,10,13, 16))+
  # ylim(0.5,5.2)+
  labs(x = "Horizon", y = "RMSE (QSU)", color = "Model ID", linetype = "Model Type")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 12),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  guides(linetype = guide_legend(nrow = 2))+
  #theme(legend.text = element_text(size = 8), legend.title = element_text(size = 10))+
  scale_color_manual(values = model_colors)+  scale_linetype_manual(values = model_shape)

#RMSE persistence skill plot
skill_for_join <- skill_df |> 
  filter(metric == "rmse",
         Null == "Skill_Peristence") |> 
  #filter(!site_id == "Across Sites") |> 
  ggplot(aes(x = Horizon, y = value, color = model_idA))+
  geom_line()+
  facet_grid(~factor(site_id, levels = c("Across Sites", "BVR", "CCR", "FCR")), scales = "free_y")+
  geom_hline(yintercept = 0, linewidth =1.2, linetype = 2)+
  geom_line(linewidth = 1.2)+
  # scale_x_continuous(breaks = c(1,4,7,10,13,16))+ 
  #guides(colour = guide_legend(nrow = 2))+
  labs(x = "Horizon", y = "Forecast Skill", color = "Model ID")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 12),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = model_colors)

rmse_skill_combo <- ggpubr::ggarrange(rmse_for_join, skill_for_join, ncol = 1, labels = "auto")

rmse_skill_combo

#ggsave("../Figures/RMSE_and_Skill_combo_MS.png", rmse_skill_combo, height = 6, width = 6.1, units = "in")



```



## RMSE and Skill Stats


```{r}

#look at interactive plots

plotly::ggplotly(skill_rmse_plot)
plotly::ggplotly(skill_crps_plot)

plotly::ggplotly(rmse_for_join)
plotly::ggplotly(skill_for_join)


```



across sites and horizon

```{r}

## CRPS
Scored_forecasts |> 
   group_by(model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |>     pivot_longer(-c(1:3)) |>
  filter(name == "CRPS") |>
  group_by(model_id, name) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    )

##RMSE
Scored_forecasts |> 
   group_by(model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |>     pivot_longer(-c(1:3)) |>
  filter(name == "RMSE") |>
  group_by(model_id, name) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    )

##SD
Scored_forecasts |> 
   group_by(model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |>     pivot_longer(-c(1:3)) |>
  filter(name == "SD") |>
  group_by(model_id, name) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    )


## SKill; use plotly plots above
skill_df |> 
  filter(Null == "Skill_Peristence") |> 
  select(site_id, Horizon, model_idA, metric, Null, value)  |> 
  filter(metric == "rmse") |> 
  group_by(site_id, model_idA) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    )



```


Make table for MS

```{r}
#figure
rbind(c,d) |> 
  filter(!name %in% c("MAE")) |> 
ggplot(aes(x = Horizon, y = value, color = model_id, linetype = model_type))+
  geom_line(linewidth = 1.2)+
  facet_grid(name~factor(site_id, levels = c("Across Sites","BVR", "CCR", "FCR")), scales = "free_y")+
  labs(x = "Horizon", y = "Metric (QSU)")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 12))+
  guides(linetype = guide_legend(nrow = 2))+
  theme(legend.text = element_text(size = 8), legend.title = element_text(size = 10))+
  scale_color_manual(values = model_colors)+  scale_linetype_manual(values = model_shape)


########################################## RMSE  #

#across sites and all models 
rbind(c,d) |> 
  group_by(site_id, model_id, name) |> 
  filter(name == "RMSE") |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    ) |> 
  select(site_id, model_id, name, median, min, max, range)


#across sites and models 
rbind(c,d) |> 
  group_by(site_id, name) |> 
  filter(name == "RMSE") |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    ) |> 
  select(site_id, name, median, min, max, range)


############################## CRPS #
#across sites and all models 
rbind(c,d) |> 
  group_by(site_id, model_id, name) |> 
  filter(name == "CRPS") |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    ) |> 
  select(site_id, model_id, name, median, min, max, range)


#across sites and models 
rbind(c,d) |> 
  group_by(site_id, name) |> 
  filter(name == "CRPS") |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    ) |> 
  select(site_id, name, median, min, max, range)



```


reservoir specific

```{r}

#RMSE horizon across reservoirs 
Scored_forecasts |> 
   group_by(site_id, model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |>     pivot_longer(-c(1:4)) |>
  filter(name == "SD") |> 
  group_by(model_id, name) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1), median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),        range = max - min    )

#RMSE horizon by reservoir
Scored_forecasts |> 
   group_by(site_id, model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |> 
    pivot_longer(-c(1:4)) |>  filter(name == "RMSE") |> 
  group_by(site_id, model_id, name) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1),  median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),       range = max - min           )

#by reservoir no model ID or horizon
Scored_forecasts |> 
   group_by(site_id, model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = mean(crps, na.rm = T),
             SD = mean(sd, na.rm = T)
            ) |> 
    pivot_longer(-c(1:4)) |>  filter(name == "CRPS") |> 
  group_by(site_id, name) |>   summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1),      median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),      range = max - min        )



#### show 16days as columns 
Scored_forecasts |> 
   group_by(site_id, model_id, model_type, Horizon) |> 
   summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 1),
             #MAE = mean(abs(mean - observation), na.rm = T),
             CRPS = round(mean(crps, na.rm = T), 1),
             SD = mean(sd, na.rm = T)
            ) |> 
    pivot_longer(-c(1:4)) |>  filter(name == "CRPS") |> 
  filter(model_id %in% c("TS_AR", "Persistence")) |> 
  pivot_wider(names_from = Horizon, values_from = value)


```



Skill stats 

```{r}
### Horizons as column names
skill_horizon <- skill_df |> 
  mutate(value = round(value, 1)) |> 
  mutate(NullA = ifelse(Null == "Skill_Climatology", "DOY", "Persistence")) |> 
  select(site_id, Horizon, model_idA, metric, NullA, value) |> 
  pivot_wider(names_from = Horizon, values_from = value) |> 
  arrange(site_id, model_idA, metric, NullA)

skill_horizon

skill_horizon |>
  filter(
    #site_id %in% c("Across Sites"),
    model_idA == "TS_AR",
    metric == "rmse", NullA == "Persistence"
  )



```



## Seasons Figure and Stats

```{r}
#### make seasons groupings 
Scored_forecasts_seasons <- Scored_forecasts |> 
   mutate(month = month(datetime),
         Season2 = ifelse(month %in% c(3,4,5), "Spring", NA),
         Season2 = ifelse(month %in% c(6,7,8), "Summer", Season2),
         Season2 = ifelse(month %in% c(9,10,11), "Fall", Season2),
         Season2 = ifelse(month %in% c(1,2,12), "Winter", Season2)
         ) 



####Get data for seasons with across reservoirs panel 

e <- Scored_forecasts_seasons |> 
  group_by(Horizon, site_id, model_id, model_type, Season2) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2))

f <- Scored_forecasts_seasons |> 
  group_by(Horizon, model_id, model_type, Season2) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2)) |> 
  mutate(site_id = "Across Sites")




## SI figure all models across seasons and sites

rmse_season_v2 <- rbind(e,f) |> 
  ggplot(aes(x = Horizon, y = RMSE, color = model_id, linetype = model_type))+ # color = model_id
  geom_line(linewidth = 1.2)+
  facet_grid(factor(site_id, levels = c("BVR", "CCR", "FCR", "Across Sites"))
             ~
               factor(Season2, levels = c("Winter", "Spring", "Summer", "Fall" )))+
  # scale_x_continuous(breaks = c(1,4,7,10,13,16))+
  labs(x = "Horizon", y = "RMSE (QSU)")+
  guides(linetype = guide_legend(nrow = 2))+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 14),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = model_colors)+ scale_linetype_manual(values = model_shape)

rmse_season_v2

#ggsave("../Figures/rmse_season_SI.png", rmse_season_v2, height = 5.5, width = 6.5, units = "in")



#### MS figure across models by season and site
rmse_seasons_avgModels <- rbind(e,f) |> 
  ungroup() |> 
  group_by(Horizon, site_id, Season2) |> 
  reframe(RMSE = mean(RMSE, na.rm = T)) |> 
  ggplot(aes(x = Horizon, y = RMSE, color = site_id))+ 
  geom_line(linewidth = 1.2)+
  facet_wrap(~factor(Season2, levels = c("Winter", "Spring", "Summer", "Fall" )), ncol = 4)+
  # scale_x_continuous(breaks = c(1,4,7,10,13,16))+
  labs(x = "Horizon", y = "RMSE (QSU)")+
  guides(linetype = guide_legend(nrow = 2))+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 14),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = c("FCR" = "#009E73", "BVR" = "orange", "CCR" = "skyblue", "Across Sites" = "black"))

rmse_seasons_avgModels

#ggsave("../Figures/rmse_season_modelAVG.png", rmse_seasons_avgModels, height = 3.5, width = 6, units = "in")



```


Seasons stats 

```{r}

#######OLD 

#seasons
Scored_forecasts_seasons |> 
  group_by(model_id, Season2, site_id) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2)) |> 
  pivot_wider(names_from = Season2, values_from = RMSE)


#just season 
Scored_forecasts_seasons |> 
  group_by(Season2, Horizon) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
            CRPS = round(mean(crps, na.rm = T),2)) |> 
  pivot_longer(-c(1:2)) |> 
  group_by(name, Season2) |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1),      median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),      range = max - min        )



#season and site
Scored_forecasts_seasons |> 
  group_by(site_id, Season2, Horizon) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
            CRPS = round(mean(crps, na.rm = T),2)) |> 
  # pivot_wider(names_from = Season2, values_from = CRPS) |> 
  pivot_longer(-c(1:3)) |> 
  group_by(name, site_id, Season2) |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1),      median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),      range = max - min        )


#just season
Scored_forecasts_seasons |> 
  group_by(site_id, Season2, Horizon) |> 
  summarise(RMSE = round(sqrt(mean((mean - observation)^2, na.rm = TRUE)), 2),
            CRPS = round(mean(crps, na.rm = T),2)) |> 
  # pivot_wider(names_from = Season2, values_from = CRPS) |> 
  pivot_longer(-c(1:3)) |> 
  group_by(name,  Season2) |> 
  summarise(min = round(min(value, na.rm = T),1),
            mean = round(mean(value, na.rm = T),1),      median = round(median(value, na.rm = T),1),
            max = round(max(value, na.rm = T),1),      range = max - min        )



##### NEW 
rbind(e,f) |> 
  ungroup() |> 
  group_by(Horizon, site_id, Season2) |> 
  reframe(RMSE = mean(RMSE, na.rm = T)) |> 
  group_by(site_id, Season2) |> 
  summarise(min = round(min(RMSE, na.rm = T),1),
            mean = round(mean(RMSE, na.rm = T),1),      median = round(median(RMSE, na.rm = T),1),
            max = round(max(RMSE, na.rm = T),1),      range = max - min        )



```



## Example forecast plots

```{r}

###set up data for example
weekbefore <- Scored_forecasts |> 
    filter(datetime <= ymd("2024-07-15"),
           datetime >= ymd("2024-07-15") - 7) |> 
  select(datetime, observation, model_id, site_id)

example_forecast_data <- Scored_forecasts |> 
  filter(reference_datetime == ymd("2024-07-15"))
  

### Example for MS 
example_4cast <- example_forecast_data |> 
  plyr::rbind.fill(weekbefore) |> 
  mutate(observation = ifelse(datetime > ymd("2024-07-15"), NA, observation)) |> 
  ggplot()+
  geom_point(aes(datetime, observation)) +
  geom_vline(aes(xintercept = as.Date("2024-07-15")))+
  geom_ribbon(aes(x = datetime, ymin = quantile02.5, ymax = quantile97.5, fill = model_id), alpha = 0.2)+
  geom_line(aes(x = datetime, y = mean, color = model_id))+
  facet_wrap(~site_id, scales = "free", nrow = 3) +
  labs(x = 'Date', y = 'fDOM (QSU)', fill = "model", color = "model") +
  # ylim(0,40)+
  # guides(x =  guide_axis(angle = 30)) +
  guides(fill = guide_legend(nrow = 6))+
  theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ #theme(legend.position = "right", text = element_text(size = 14), legend.text = element_text(size =12))+
  scale_fill_manual(values = model_colors)+scale_color_manual(values = model_colors)

example_4cast

#ggsave("../Figures/Example_4cast.png", example_4cast, width = 5.5, height = 3.5, units = "in")


#### Examples for workflow figure

#figure where just one model at one reservoir; NO evaluation
example_workflow <-  example_forecast_data |> 
  plyr::rbind.fill(weekbefore) |> 
  filter(site_id == "FCR", model_id == "TS_AR") |> 
  mutate(observation = ifelse(datetime > ymd("2024-07-15"), NA, observation)) |> 
  ggplot()+
  geom_point(aes(datetime, observation)) +
  geom_vline(aes(xintercept = as.Date("2024-07-15")))+
  geom_ribbon(aes(x = datetime, ymin = quantile02.5, ymax = quantile97.5), alpha = 0.2)+
  geom_line(aes(x = datetime, y = mean))+
  labs(x = 'Date', y = 'fDOM (QSU)', fill = "model", color = "model") +
  guides(fill = guide_legend(nrow = 6))+
  theme_bw() + theme(text = element_text(size = 18))+
  scale_fill_manual(values = model_colors)+scale_color_manual(values = model_colors)

example_workflow

#ggsave("../Figures/Ex_4cast_workflow.png", example_workflow, width = 2.8, height = 3, units = "in")



#figure where just one model at one reservoir; YES evaluated
example_workflow_eval <-  example_forecast_data |> 
  plyr::rbind.fill(weekbefore) |>
  filter(site_id == "FCR", model_id == "TS_AR") |> 
  ggplot()+
  geom_point(aes(datetime, observation)) +
  geom_vline(aes(xintercept = as.Date("2024-07-15")))+
  geom_ribbon(aes(x = datetime, ymin = quantile02.5, ymax = quantile97.5), alpha = 0.2)+
  geom_line(aes(x = datetime, y = mean))+
  labs(x = 'Date', y = 'fDOM (QSU)', fill = "model", color = "model") +
  guides(fill = guide_legend(nrow = 6))+
  theme_bw() + theme(text = element_text(size = 18))+
  scale_fill_manual(values = model_colors)+scale_color_manual(values = model_colors)

example_workflow_eval

#ggsave("../Figures/Ex_4cast_workflow_eval.png", example_workflow_eval, width = 2.8, height = 3, units = "in")


```



## Observed fDOM TS

Plots of observed daily data 

```{r}
#all on one plot
targets <- read_csv("../Data/GeneratedData/Targets_fDOM_allReservoirs.csv")

fdom_TS <- targets |> 
  filter(#datetime >= ymd("2023-03-13"),
         datetime >= ymd("2024-03-01")
         # datetime < ymd("2024-12-01")
         ) |> 
  mutate(site_id_A = ifelse(site_id == "fcre", "FCR", NA),
         site_id_A = ifelse(site_id == "bvre", "BVR", site_id_A),
         site_id_A = ifelse(site_id == "ccre", "CCR", site_id_A)) |> 
  ggplot(aes(x = datetime, y = observation, color = site_id_A))+
  # geom_rect(aes(xmin = ymd("2023-03-13"), xmax = ymd("2023-12-01"), ymin = -Inf, ymax = Inf), 
  #           alpha = 0.01, fill = "gray", color = NA )+ 
  #  annotate("text", x = as.Date("2023-07-15"), y = 30, label = "Calibration", color = "black", size = 4, fontface = "bold")+
  #  annotate("text", x = as.Date("2024-07-15"), y = 30, label = "Forecasting", color = "black", size = 4, fontface = "bold")+
  geom_point()+
  # annotate(geom = "point", x = ymd("2023-11-01"), y = 28, shape = 15, size = 3, color = "#009E73", alpha = 0.7)+
  # annotate(geom = "point", x = ymd("2023-11-02"), y = 27.7, shape = 15, size = 3, color = "orange", alpha = 0.7)+
  # annotate(geom = "point", x = ymd("2023-11-14"), y = 28, shape = 15, size = 3, color = "skyblue", alpha = 0.7)+
  # annotate(geom = "point", x = ymd("2024-03-02"), y = 28, shape = 17, size = 3, color = "#009E73", alpha = 0.7)+
  # annotate(geom = "point", x = ymd("2024-03-01"), y = 28, shape = 17, size = 3, color = "orange", alpha = 0.7)+
  # annotate(geom = "point", x = ymd("2024-03-03"), y = 28, shape = 17, size = 3, color = "skyblue", alpha = 0.7)+
  scale_x_date(date_breaks = "1 month", date_labels = "%b" )+
  scale_y_continuous(limits = c(3,28), breaks = c(5,10,15,20,25))+
  labs(x = "Date", y = "fDOM (QSU)", color = "Reservoir")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = c("FCR" = "#009E73", "BVR" = "orange", "CCR" = "skyblue"))

fdom_TS

#ggsave("../Figures/Observed_FDOM_TS.png", fdom_TS, height = 4, width = 6.5, units = "in")



#### Turnover and Helene plot (calling Helene landfall 024-09-26)

turnover_helene_plot <- targets |>
  filter(datetime >= ymd("2024-09-01"),
         datetime < ymd("2024-12-01") ) |>
  mutate(site_id_A = ifelse(site_id == "fcre", "FCR", NA),
         site_id_A = ifelse(site_id == "bvre", "BVR", site_id_A),
         site_id_A = ifelse(site_id == "ccre", "CCR", site_id_A)) |>
  ggplot(aes(x = datetime, y = observation, color = site_id_A))+
  geom_point()+ geom_vline(xintercept = ymd("2024-09-26"))+
  annotate(geom = "point", x = ymd("2024-10-28"), y = 22, shape = 15, size = 3, color = "#009E73")+
  annotate(geom = "point", x = ymd("2024-11-16"), y = 22, shape = 15, size = 3, color = "orange")+
  annotate(geom = "point", x = ymd("2024-11-03"), y = 22, shape = 15, size = 3, color = "skyblue")+
  labs(x = "Date", y = "fDOM (QSU)", color = "Reservoir")+
  theme_bw() + theme(legend.position = "top", text = element_text(size = 18),
                    panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_manual(values = c("FCR" = "#009E73", "BVR" = "orange", "CCR" = "skyblue"))

turnover_helene_plot
plotly::ggplotly(turnover_helene_plot)

###Helene numbers
##CCR fDOM level rises from 6.7 to 12.8 QSU (6.7 QSU) between 25sep24 (day before) and 6oct24 (10 days after)
##BVR fDOM level rises from 14.2 to 15.4 QSU (1.2 QSU) between 25sep24 (day before) and 6oct24 (10 days after)
##FCR fDOM level rises from 17.6 to 26.3 QSU (8.7 QSU) between 25sep24 (day before) and 6oct24 (10 days after)

###Turnover numbers



```

Summary stats of observed data

```{r}
## Summary stats 
targets |> 
  filter(#datetime >= ymd("2023-03-13"),
         datetime >= ymd("2024-03-01")
         # datetime < ymd("2024-12-01")
         ) |> 
  group_by(site_id) |> 
  summarise(min = round(min(observation, na.rm = T), 1),
            median = round(median(observation, na.rm = T), 1),
            mean = round(mean(observation, na.rm = T), 1),
            max = round(max(observation, na.rm = T), 1),
            sd = round(sd(observation, na.rm = T), 1),
            range = max - min) |> 
  mutate(CV = round((sd/mean), 2)*100)


#cleaned stats for full year for table in MS 
targets |> 
  filter(#datetime >= ymd("2023-03-13"),
         datetime >= ymd("2024-03-01")
         # datetime < ymd("2024-12-01")
         ) |> 
  group_by(site_id) |> 
  summarise(min = round(min(observation, na.rm = T), 1),
            median = round(median(observation, na.rm = T), 1),
            mean = round(mean(observation, na.rm = T), 1),
            max = round(max(observation, na.rm = T), 1),
            sd = round(sd(observation, na.rm = T), 1),
            range = max - min,
            range_A = paste(min, max, sep = " - ")) |> 
  mutate(CV_percent = round((sd/mean), 2)*100) |> 
  select(site_id, median, range_A, CV_percent)

#cleaned stats for full year by seasons for table in MS 
targets |> 
     mutate(month = month(datetime),
         Season2 = ifelse(month %in% c(3,4,5), "Spring", NA),
         Season2 = ifelse(month %in% c(6,7,8), "Summer", Season2),
         Season2 = ifelse(month %in% c(9,10,11), "Fall", Season2),
         Season2 = ifelse(month %in% c(1,2,12), "Winter", Season2)
         ) |> 
  filter(#datetime >= ymd("2023-03-13"),
         datetime >= ymd("2024-03-01")
         # datetime < ymd("2024-12-01")
         ) |> 
  group_by(site_id, Season2) |> 
  summarise(min = round(min(observation, na.rm = T), 1),
            median = round(median(observation, na.rm = T), 1),
            mean = round(mean(observation, na.rm = T), 1),
            max = round(max(observation, na.rm = T), 1),
            sd = round(sd(observation, na.rm = T), 1),
            range = max - min,
            range_A = paste(min, max, sep = " - ")) |> 
  mutate(CV_percent = round((sd/mean), 2)*100) |> 
  select(site_id, Season2, median, range_A, CV_percent) |> 
  mutate(median = as.character(median),
         CV_percent = as.character(CV_percent)) |> 
  pivot_longer(-c(1:2)) |> 
  pivot_wider(names_from = Season2, values_from = value)



```


Calculate turnover dates; FCR and BVR

```{r}
# targets_url <- "https://renc.osn.xsede.org/bio230121-bucket01/vera4cast/targets/project_id=vera4cast/duration=P1D/daily-insitu-targets.csv.gz"
# 
# #### FCR
# ##FCR 2023-11-01 mixes: 2024-03-02 re strats; 2024-10-28 mixes
# fcre_turnover <- read_csv(targets_url) |>
#   select(-project_id, -duration) |>
#   filter(site_id == "fcre",
#          depth_m %in% c(0.1, 9)) |>
#   filter(variable == "Temp_C_mean",
#          datetime > ymd("2023-04-13")) |>
#   pivot_wider(names_from = depth_m, values_from = observation) |>
#   rename(wtr_01 = 5,
#          wtr_9 =4) |>
#   mutate(Temp_diff = wtr_01 - wtr_9)
# 
# 
# #### BVR
# ##BVR - 2023-11-01 mixes: 2024-03-02 re strats; 2024-11-16 mixes
# bvre_turnover <- read_csv(targets_url) |>
#   select(-project_id, -duration) |>
#     filter(variable == "Temp_C_mean",
#          datetime > ymd("2023-04-13"),
#          site_id == "bvre") |>
#   filter(depth_m > 9 | depth_m < 1) |>
#   pivot_wider(names_from = depth_m, values_from = observation) 
#
#
# #### CCR
# ccrgit <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/ccre-dam-data-qaqc/ccre-waterquality_L1.csv")
# ccredi <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/1069/3/4afb209b30ebed898334badd3819d854")
# ccrfull <- rbind(ccredi, ccrgit)
# 
# ccr_turnover <- ccrfull |>
#   select(3:16) |>
#   mutate(Date = as.Date(DateTime)) |>
#   select(-c(1,7:12)) |>
#   group_by(Date) |>
#   summarise(across(everything(), list(mean))) |>
#   filter(Date > ymd("2023-03-13")) |>
#   mutate(T1_T13 = ThermistorTemp_C_1_1 - ThermistorTemp_C_13_1,
#          T2_T13 = ThermistorTemp_C_2_1 - ThermistorTemp_C_13_1,
#          T3_T13 = ThermistorTemp_C_3_1 - ThermistorTemp_C_13_1,
#          T4_T13 = ThermistorTemp_C_4_1 - ThermistorTemp_C_13_1,
#          T5_T13 = ThermistorTemp_C_5_1 - ThermistorTemp_C_13_1)
# 
# 
# #CCR mixes: 2023-11-14; restrats 2024-03-03; mixes 2024-11-03
# #these and FCR and BVR defined as mixing first day top and bottom temp are < 1C; strat as first day that top and bottom are > 1C and remains for 2 weeks


```


get water level data 

```{r}
fcredi <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/271/9/f23d27b67f71c25cb8e6232af739f986")
fcrgit <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/refs/heads/fcre-catwalk-data-qaqc/fcre-waterquality_L1.csv")

bvredi <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/725/5/f649de0e8a468922b40dcfa34285055e")
bvrgit <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/BVRE-data/refs/heads/bvre-platform-data-qaqc/bvre-waterquality_L1.csv")

ccredi <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/1069/3/4afb209b30ebed898334badd3819d854")
ccrgit <- read_csv("https://raw.githubusercontent.com/FLARE-forecast/CCRE-data/refs/heads/ccre-dam-data-qaqc/ccre-waterquality_L1.csv")

```

water level data and plots 

```{r}
#### BVR
bvrdepth <- rbind(bvredi, bvrgit) |> 
  mutate(Date = as.Date(DateTime)) |> 
  group_by(Date) |> 
  summarise(depth = mean(LvlDepth_m_13, na.rm = T)) |> 
  filter(Date >= ymd("2024-03-01"),
         Date <= ymd("2025-03-01"))

summary(bvrdepth)

depth_bvrplot <- bvrdepth |> 
  ggplot(aes(x = Date, y = depth)) + geom_point() + geom_vline(xintercept = ymd("2024-09-26"))+ ggtitle("BVR")
plotly::ggplotly(depth_bvrplot)
##BVR water level rises from 9.89 to 10.30 (0.4m) between 25sep24 (day before) and 6oct24 (10 days after helene)


#### CCR
ccrdepth <- rbind(ccredi, ccrgit) |> 
  mutate(Date = as.Date(DateTime)) |> 
  group_by(Date) |> 
  summarise(depth = mean(LvlDepth_m_13, na.rm = T)) |> 
  filter(Date >= ymd("2024-03-01"),
         Date <= ymd("2025-03-01"))

summary(ccrdepth)

depth_ccrplot <- ccrdepth |> 
  ggplot(aes(x = Date, y = depth)) + geom_point() + geom_vline(xintercept = ymd("2024-09-26"))+ ggtitle("CCR")
plotly::ggplotly(depth_ccrplot)
##CCR water level rises from 17.26 to 18.48 (1.2m) between 25sep24 (day before) and 6oct24 (10 days after helene)


#### FCR
fcrdepth <- rbind(fcredi, fcrgit) |> 
  mutate(Date = as.Date(DateTime)) |> 
  group_by(Date) |> 
  summarise(depth = mean(LvlDepth_m_9, na.rm = T)) |> 
  filter(Date >= ymd("2024-03-01"),
         Date <= ymd("2025-03-01"))

summary(fcrdepth)

depth_fcrplot <- fcrdepth |> 
  ggplot(aes(x = Date, y = depth)) + geom_point() + geom_vline(xintercept = ymd("2024-09-26"))+ ggtitle("FCR")
plotly::ggplotly(depth_fcrplot)
##FCR water level rises from 9.17 to 9.18  (0.01 m) between 25sep24 (day before) and 6oct24 (10 days after helene)
## But peaked at 9.29m on 28sep24 (0.1m)


```












